The Mass Relations between Supermassive Black Holes and Their Host Galaxies using Eight Strongly Lensed AGN Systems.

### 2020-03-09 manuscript/manuscript.tex
update paper

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[X. Ding et al.]{
Xuheng Ding,$^{1}$\thanks{E-mail: dxh@astro.ucla.edu}
Tommaso Treu,$^{1}$
Simon Birrer,$^{1, 2}$
Dominique Sluse,\newauthor
Chris Fassnacht,
Matthew W. Auger,
Sherry H. Suyu,
Kenneth C. Wong,\newauthor
Takahiro Morshita,
and et al. $^{3}$
\\
% List of institutions
$^{1}$Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA\\
$^{2}$Kavli Institute for Particle Astrophysics and Cosmology and Department of Physics, Stanford University, Stanford, CA 94305, USA\\
$^{3}$xxx
}

@@

% Abstract of the paper
\begin{abstract}
Strong lensed AGN has been considered as a unique tool to exam the correlations between the mass of the supermassive Black Hole and its host galaxies. In this work, we have adopted eight strongly lensed system from the H0LiCOW collaboration. The deep \hst\ data and adopt the \lenstronomy\ to reconstruct the image of the source. The \mbh\ are estimated using the board emission line. We compare our inference to the once in the literature and find a consistent result. Combining them together, we are able to constrain the $\gamma$ to xxx. Our our demonstrate is demonstrate the power of using strong lensed AGNs. The sample of the data are supposed to increase rapidly.
\end{abstract}

@@

\section{Introduction}
Structure:

[] What is scaling relations.

[] Strong lensing provide a tool to study to higher redshift.

[] Previous work. H0LiCOW XI. H0LiCOW XII. In these two works, the host galaxy is first reconstructed using the pixellation. Then, the host image are inferred in the source plan by fitting as a \sersic\ model. This means, the two-step inference of the host information.

[] In this work, we adopt an independent tool and carry out a direct inference of the host properties.

[]This paper is organized as follows. Zeropoint are defined in the AB systems.

\section{Sample Selection}
We adopt the eight lens systems from our H0LiCOW collaboration including HE~0435$-$1223, RXJ~1131$-$1231, WFI~2033$-$4723, HE~1104$-$1805, SDSS~1206$+$4332, SDSS~0246$-$0825, HE~0047$-$1756 and HS~2209$+$1914. For conciseness, we abbreviate each lens name to four digits (e.g., RXJ~1131$-$1231 to RXJ1131). In \citet{Ding2017a}, the simulation exercise has been performed to understand the fidelity of the source reconstruction based on these eight systems and verified that the host inference is trustworthy when its magnitude are brighter than 20 magnitude, 2$-$4 magnitudes dimmer than the AGN. The detailed information of the observational conditions of our eight systems are given in Table~\ref{data_set}. Besides the adopted filter shown therein, some systems also observed by \hst\ by different bands. As will shown in Section~\ref{sec:mstar}, the multi-band information enables us to apply the stellar population, hence a more accurate \mstar\ estimation.

While we note that our sample size included eight systems, which is a limited sample to constrain the evolution of the scaling relation. In this particular work, we simply aim to plot the scaling relation of our sample and make comparison to the ones in the literature. %[]The comparison sample (32 QSO paper)
We adopt the recent efforts by~\citet{Ding2020}, including 32 AGNs at redshift range $1.2<z<1.9$, 79 redshift QSO and 55 local measurements.

@@

For each lens system, we adopt different choices to perform the fitting. The distribution of the fitting inference are assumed to sufficiently cover the truth. We then apply a statistical measurement to weighting for the final inference and estimate the uncertainty level. The different choice of the fitting including the following.
\begin{enumerate}
\item Following common practice, we select all the bright, isolated stars across the image frame of targets to define the PSF. Each selected star is consider as the initial PSF to input to the fitting, which is considered as different choice.
\item The central pixel of the AGNs are very bright and have systematic errors during the interpolation of the subsampled PSF. To avoid overfitting the noise, we adopt two modeling choices. 1)~manually boost the noise estimate in the central area to effectively infinite; 2)~perform the iterative PSF estimation as introduced by ref[].
\item To calculate the ray tracing under a higher resolution grid, the different relative level to the pixel sizes is selected, including [$2\times2$, $3\times3$] pixel$^{-1}$.
\item Using the lensing imaging alone is difficult to constrain the power-law slope. To avoid any overfitting, we fix the slope values during the lens modelling with three optional value $[1.9, 2.0, 2.1]$.
\end{enumerate}

All in all, for one lens system with a number of $N$ initial PSFs, we select in total of $N\times12$ (i.e., $2 \times2 \times3$) different choices of fitting. After  all sets of fittings are completed, we rank their performance of each choice based on their best-fitted $\chi^2$ value. Finally, we adopt the weighting algorithm as introduced by Equations (3)$-$(6) in~\citet{Ding2020} and combine the top eight choices to derive the final value and evaluate the uncertainties.

\subsection{Photometry Inference}
In this subsection, we describe the details of the fitting for each systems and present our inference of the host galaxy photometry.

@@

As a cross check, we compare our host magnitude to the measurement in Ding+2017[], in which they model the reconstructed host galaxy as \sersic\ based on Galfit []. The host magnitude measured in that paper is: $mag = 21.75 \pm 0.13$%, $R_{eff} = 0.82 \pm 0.14$ and $n = 3.94 \pm 0.14$. 
which is slightly fainter than our results, i.e. $mag = 21.33 \pm 0.2$. \ding{Some discussion of the origin of this offset?}
Still, the center mismatch is only $0.15$~dex, which is a little of the total error budget.

@@

We also compare our measurement to the previous reconstructions in Ding. Based on the reconstructions by Suyu[], the inference of the host magnitude by Ding[] is $mag_{\rm disk} = 20.07\pm0.06$ and $mag_{\rm bulge} = 21.81 \pm 0.28$. Compared to our inference in Table~\ref{tab:host_measure}, our inferred bulge flux is consistent at $\sim0.25$ dex level, however, while the inferred disk light is much brighter by $\sim 0.7$ dex.

@@

The final inference are presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(c). We also compare the inference to the reconstructions by Ken. Fitting their reconstruction as a \sersic\ profile, we have inferred that $mag = 21.98 \pm 0.15$ which is slightly fainter than our inference by $\sim0.2$~dex.

\subsubsection{SDSS1206}
SDSS1206 is a special system -- the AGN is a doubly images while most of the host is falls inside the inner caustic thus being quadruply imaged. We consider the galaxy triplet group at the north-west and use a single SIS model to denote their over all mass perturbations. Moreover, as noted by Simon[] (Figure 1 therein), a sub-clump is located in the north which is hardly visible. We model it as a SIS mass model and circular \sersic\ light model with joint centroids. Though we see the visible residuals in the fitted arcs using a single \sersic\ model, we find a double \sersic\ could help significantly improve the goodness of the fitting. Thus, we adopt the single \sersic\ model in our final inference.

@@

\subsubsection{HS2209}
The inference of this system is summarized in Figure~\ref{fig:image_inference}-(g). \ding{The host magnitude might be overestimated. The QSO is over bright with a positive background light. Xuheng is Re-fitting this image.}

@@

\begin{table*}
\renewcommand{\arraystretch}{1.25}
%\setlength{\tabcolsep}{20pt}
\centering
  \begin{threeparttable}
\caption{Summary of lensed AGN inference.}\label{tab:host_measure}    
%\resizebox{12cm}{!}{
     \begin{tabular}{ccccccc}
\hline     
(1) & (2) & (3) & (4) & (5) & (6) & (7) \\    
Object ID & Magnitude & Flux Ratio (to Total) & \reff\ & \sersic\ $n$ & adopted AGE & $\log (M_{*}$)  \\
 & (AB system) & ($\%$) & (arcsec) & & (Gyr) & (M$_{\odot}$) \\ \hline
HE0435 & $21.492\substack{+0.402\\-0.293}$ & $35.981\pm11.127$ & $0.279\pm0.023$ & $2.710\pm0.204$ & $1.500$ & $10.91\substack{+0.12\\-0.16}$ \\
RXJ1131$_{\rm bulge}$ & $22.092\substack{+0.221\\-0.183}$ & $6.658\pm1.225$ & $0.107\pm0.014$ & fix to 4 & $3.000$ & $10.27\substack{+0.07\\-0.09}$ \\
RXJ1131$_{\rm disk}$ & $19.495\substack{+0.159\\-0.138}$ & $72.816\pm9.892$ & $0.845\pm0.049$ & fix to 1 & $1.500$ & $11.01\substack{+0.06\\-0.06}$ \\
WFI2033 & $21.781\substack{+0.285\\-0.225}$ & $19.645\pm4.534$ & $0.280\pm0.017$ & $0.524\pm0.013$ & $0.625$ & $10.51\substack{+0.09\\-0.11}$ \\
SDSS1206 & $21.310\substack{+0.232\\-0.191}$ & $33.302\pm6.413$ & $0.112\pm0.021$ & $4.568\pm0.530$ & $0.625$ & $10.77\substack{+0.08\\-0.09}$ \\
HE1104 & $21.252\substack{+0.163\\-0.142}$ & $13.990\pm1.953$ & $0.270\pm0.023$ & $1.048\pm0.045$ & $0.625$ & $11.05\substack{+0.06\\-0.07}$ \\
SDSS0246 & $23.437\substack{+0.279\\-0.222}$ & $3.978\pm0.901$ & $0.436\pm0.084$ & $4.964\pm0.081$ & $0.626$ & $10.75\substack{+0.09\\-0.11}$ \\
HS2209 & $20.200\substack{+0.128\\-0.114}$ & $21.108\pm2.348$ & $3.116\pm1.834$ & $3.302\pm0.521$ & $1.001$ & $11.25\substack{+0.05\\-0.05}$ \\
HE0047 & $22.923\substack{+0.485\\-0.334}$ & $2.347\pm0.845$ & $0.319\pm0.146$ & $4.176\pm0.750$ & $0.625$ & $10.91\substack{+0.13\\-0.19}$ \\
\hline
\end{tabular}
%}
\begin{tablenotes}
      \small
      \item Note: $-$ If any
\end{tablenotes}    
\end{threeparttable}
\end{table*}

@@

\subsection{Population and stellar mass}\label{sec:mstar}
%[] Color inference for the first three cases to decide their stellar template. 
Besides the band we imaging data at the given band we studied in last section, some of the systems also have other band observations by the \hst, which provides the color information of the host galaxy. Given that the other band data has less exposure time with lower single to noise level, we highlight that we only study the color to find a decent stellar template. Then, it would be adopted to the host photometry obtained in last section to infer the final stellar mass.

{\bf HE0435} ~ Besides WFC3/F160W, HE0435 has also been observed by the \hst\ through ACS/F814W and ACS/F555W (GO-xxxx; PI: xxxx). We adopted the same approaches to modeling the data separately at these two band. % The inferred host magnitudes are xxx and xxx, respectively.
Considering that the lensed arcs is mainly inferred by the subtraction of the AGNs and deflectors light, it is less dependent on the lens model and thus can be obtained more accurately. Thus, we infer the color of the lensed arcs in the image plane. We use {\sc Gsf} code to fit the magnitude of the lensed host and find a 1.5 Gyr stellar template with solar metallicity could well match this color. More details of the information could be found in the Appendix~\ref{app:HE0435}.

{\bf RXJ1131} ~ For this system, the lensed arc is very extended in the image plane which is resolved to the AGNs, one could directly perform the SED fitting of the arc in the image plane. Combining the \hst\ imaging data through F814W and F555W (GO-9744; PI: C. S. Kochanek), we inference the color and we adopt the stellar templates 3 Gyr and 1.5 Gyr with solar metallicity stellar to its disk and bulge, respectively (see Appendix~\ref{app:RXJ1131} for the inference).

{\bf WFI2033} ~ Besides the F160W filter, four filters including F125W, F140W, F555W and F814W has been employed to obtain the imaging data. We perform the lens model inference for all the filter and infer the host color through five band in the image plane. We find a stellar template with 0.625 Gyr could well match their color (Appendix~\ref{app:WFI2033}).

{\bf HE1104 and other systems} ~ The HE1104 has been observed through F555W and F814W band. However, given the faint and the limited exposure time, the signal of the lensed arcs at the other band is not visible. There is no other band for the other systems. For these systems, we adopt the criteria by Ding2020[] to assign their stellar population, i.e., the 1 Gyr and 0.625 Gyr stellar population would be adopted for systems as $z<1.44$ and $z>1.44$, respectively.

A summary of the adopted stellar populations is given in Table~\ref{tab:host_measure}, column~(7). Applying these templates to the filter magnitudes obtained in last section, we obtain the stellar mass of our system. The uncertainty of the \mstar\ are considered as 0.2 dex, and as studied in~\citet{Ding2017a}, we expect that the uncertainty of the \mbh\ dominate the error budget.

\subsection{The \mbh-\mstar\ relation}\label{sec:relation}
We combine the measured \mstar\ to their \mbh\ and plot their scaling relations among the recent measurements by \citet{Ding2020}, shown in Figures. The result demonstrate an excellent consistency. and the result support the evolution. 
We combine the \mstar\ to their \mbh\ and compare to the ones in the literature.

@@

@@

\section{Color inference of the host}
We took the other band data and get the only arc image. We adopt these image and do the SED fitting to get the color information.
\subsection{HE0435}\label{app:HE0435}
The HE0435 system has been modelled through three band. In the Figure, we demonstrate the host inference in the image plance for the three bands.

\begin{figure*}
\centering
\subfloat[HE0435 F555W]{\includegraphics[ width=0.8\textwidth]{fig/HE0435_f555w_inference.pdf}}\\
\subfloat[HE0435 F814W]{\includegraphics[ width=0.8\textwidth]{fig/HE0435_f814w_inference.pdf}}
\caption{\label{fig:app_HE0435} 
Illustrations of the inference for each system. On the top: (left to right): . On the bottom: (left to right.) }
\end{figure*}

\subsection{RXJ1131}\label{app:RXJ1131}
We directly preform the SED fitting in the imaging plane. The inferred AGN information is obtain in the Figure.

\subsection{WFI2033}\label{app:WFI2033}
Similar to Section~\ref{app:HE0435}, the lensed color of WFI2033 has been modelled through five band which are illustrated in the Figure.

\begin{figure*}
\centering
\subfloat[WFI2033 F125W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f125w_inference.pdf}}\\
\subfloat[WFI2033 F140W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f140w_inference.pdf}}\\
\subfloat[WFI2033 F555W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f555w_inference.pdf}}\\
\subfloat[WFI2033 F814W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f814w_inference.pdf}}
\caption{\label{fig:app_WFI2033} 
Illustrations of the inference for each system. On the top: (left to right): . On the bottom: (left to right.) }
\end{figure*} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[X. Ding et al.]{
Xuheng Ding,$^{1}$\thanks{E-mail: dxh@astro.ucla.edu}
Tommaso Treu,$^{1}$
Simon Birrer,$^{1, 2}$
Dominique Sluse,\newauthor
Chris Fassnacht,
Matthew W. Auger,
Kenneth C. Wong,
Sherry H. Suyu,\newauthor
Takahiro Morshita,
and et al. $^{3}$
\\
% List of institutions
$^{1}$Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA\\
$^{2}$Kavli Institute for Particle Astrophysics and Cosmology and Department of Physics, Stanford University, Stanford, CA 94305, USA\\
$^{3}$xxx
}

@@

% Abstract of the paper
\begin{abstract}
Strong lensed AGN has been considered as a unique tool to exam the correlations between the mass of the supermassive Black Hole and its host galaxies. In this work, we have adopted eight strongly lensed system from the H0LiCOW collaboration. The deep \hst\ data and adopt the \lenstronomy\ to reconstruct the image of the source. Using the reconstructed brightness of the host galaxy, we infer the host galaxy stellar mass based on the assumed stellar population. 
The \mbh\ are estimated using the board emission line. We compare our inference to the ones in the literature and find a consistent result. The consistent scaling resolutions derived from our sample confirm the evolution conclusion and confirm the the power of using strong lensed AGNs. The sample of the data are supposed to increase rapidly.
\end{abstract}

@@

\section{Introduction}
The tight correlations between the masses (\mbh) of supermassive black holes (BHs) and their host galaxies properties including stellar mass (\mstar), stellar velocity dispersion ($\sigma_*$) and luminosity (\lhost), known as scaling relations, are usually considered as a result of their co-evolution.

The origin of these relations is till unclear so far. In theory, cosmological simulations of structure formation are able to reproduce the local tight relation based on physical mechanism by invoking active galactic nucleus (AGN) feedback as the physical connection or having them share a common gas supply. On the other hand, without any physical coupling, the pure statistical convergence by galaxy mergers alone could also reproduce the observed correlations at local universe. It is crucial to extend the correlation studies to higher redshift and understand their evolution as a function of redshift. Recently, \citet{Ding2020} measured the scaling relations at redshift range of $1.2<z<1.7$ based on a sample of 32 AGNs using \hst/WFC3. Comparing to the published samples at local and intermediate redshift range, they confirm the an evolution scenario that the growth of BHs evolution predates than the host galaxy bulge. In the following up work, \citet{Ding2020b} used the measurements of the high-$z$ AGNs and compare to numerical simulations including the hydrodynamic simulation MassiveBlackII (MBII) and a semi-analytic model (SAM). The tightness of the scaling relation at high-$z$ supports the hypothesis that AGN feedback as a promising driver for the scaling correlations. A larger sample at higher redshift would be even more beneficial to confirm this scenario.

Benefiting from the gravitational lensing magnification and stretching effect, strong lensed AGNs provide a unique tool to make progress in this study (ref[Peng2006]), 
provided that the lens modelling is accurate. \citet{Ding2017a} has carried out extensive and realistic simulations tests based on the deep \hst\ observations for a sample of eight lens systems in H0LiCOW collaboration. This work has confirm the reconstruction of the lensed host galaxy properties can be recovered with better precision and accuracy than the typical \mbh\ uncertainty. As a following up effort, \citet{Ding2017b} has applied the advanced techniques to two strongly lensed systems to study their \mbh-\lhost\ relations and obtained consistent results to the ones in the literature.

In this work, we aim to make progress by completing the analysis of the entire eight systems. We have developed an independent approach to achieve a one-step inference of the host photometry. We adopt the a set of extended modelling choices to assure the accuracy of our measurements. Moreover, we comparing our new measurements to the ones which have been modelled by the H0LiCOW collaboration to make the cross check. 3/8 of our objects have multi-band \hst\ imaging and we are able to infer their host color to assess an accurate inference of the stellar mass. The extended range of the eight systems would help us to make a direct comparison to the latest measurements by \citet{Ding2020}. We also adopt a class of self-consistent recipes to recalibrate the \mbh\ of our sample.

This paper is organized as follows xxx. Zeropoint are defined in the AB systems. A Chabrier initial mass function (IMF) is employed consistently.

\section{Sample Selection}\label{sec:sample_select}
We adopt the eight lens systems from our H0LiCOW collaboration including HE0435$-$1223, RXJ1131$-$1231, WFI2033$-$4723, HE1104$-$1805, SDSS1206$+$4332, SDSS0246$-$0825, HE0047$-$1756 and HS2209$+$1914. For conciseness, we abbreviate each lens name to four digits (e.g., RXJ~1131$-$1231 to RXJ1131). In \citet{Ding2017a}, the simulation exercise has been performed to understand the fidelity of the source reconstruction based on these eight systems and verified that the host inference is trustworthy when its magnitude are brighter than 20 magnitude, 2$-$4 magnitudes dimmer than the AGN. The detailed information of the observational conditions of our eight systems are given in Table~\ref{data_set}. Besides the adopted filter shown therein, some systems also observed by \hst\ by different bands. As will shown in Section~\ref{sec:mstar}, the multi-band information enables us to apply the stellar population, hence a more accurate \mstar\ estimation.

While we note that our sample size included eight systems, which is a limited sample to constrain the evolution of the scaling relation. In this particular work, we simply aim to plot the scaling relation of our sample and make comparison to the ones in the literature. %[]The comparison sample (32 QSO paper)
We adopt the recent efforts by~\citet{Ding2020}, including 32 AGNs at redshift range $1.2<z<1.9$, 79 intermediate redshift QSO and 55 local measurements. It is worth noticing that they are so far the largest \hst\ imaging AGN samples with redshift range from 1.9 to the local.

@@

For each lens system, we adopt different choices to perform the fitting. The distribution of the fitting inference are assumed to sufficiently cover the truth. We then apply a statistical measurement to weighting for the final inference and estimate the uncertainty level. The different choice of the fitting including the following.
\begin{enumerate}
\item Following common practice, we select all the bright, isolated stars across the image frame of targets to define the PSF. Each selected star is consider as the initial PSF to input to the fitting, which is considered as different choice.
\item The central pixel of the AGNs are very bright and have systematic errors during the interpolation of the subsampled PSF. To avoid overfitting the noise, we adopt two different modelling options: 1)~manually boost the noise estimate in the central area to effectively infinite; 2)~perform the iterative PSF estimation as introduced by ref[].
\item To calculate the ray tracing under a higher resolution grid, the different relative level to the pixel sizes is selected, including [$2\times2$, $3\times3$] pixel$^{-1}$.
\item Using the lensing imaging alone is difficult to constrain the power-law slope. To avoid any overfitting, we fix the slope values during the lens modelling with three optional value $[1.9, 2.0, 2.1]$.
\end{enumerate}

All in all, for one lens system with a number of $N$ initial PSFs, we select in total of $N\times12$ (i.e., $2 \times2 \times3$) different choices of fitting. After  all sets of fittings are completed, we rank their performance of each choice based on their best-fitted $\chi^2$ value. Finally, we adopt the weighting algorithm as introduced by Equations (3)$-$(6) in~\citet{Ding2020}. Since there is no obvious evidence of better perform between QSO mask or PSF iteration, we selected each top-4 fitting by these to choice and combining them equally to derive the final results and to evaluate the uncertainties.

\subsection{Photometry Inference}\label{sec:photometry}
In this subsection, we describe the details of the fitting for each systems and present our inference of the host galaxy photometry.

@@

As a cross check, we compare our host magnitude to the measurement in Ding+2017[], in which they model the reconstructed host galaxy as \sersic\ based on Galfit []. The host magnitude measured in that paper is: $mag = 21.75 \pm 0.13$, %, $R_{eff} = 0.82 \pm 0.14$ and $n = 3.94 \pm 0.14$. 
which is slightly fainter than our inference, i.e. $mag = 21.50 \pm 0.35$. The offset is within $1-\sigma$ level.

@@

We also compare our measurement to the previous reconstructions in Ding. Based on the reconstructions by Suyu[], the inference of the host magnitude by Ding[] is $mag_{\rm bulge} = 21.81 \pm 0.28$ and $mag_{\rm disk} = 20.07\pm0.06$. Compared to our inference in Table~\ref{tab:host_measure}, the bulge flux is very consistent, however, while our inferred disk is brighter by $\sim 0.5$ mag. \ding{Some discussion of this offset.}

@@

The final inference are presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(c). We also compare the inference to the reconstructions by Ken. Fitting their reconstruction as a \sersic\ profile, we have inferred that $mag = 21.98 \pm 0.15$ which is also consistent to our inference.

\subsubsection{SDSS1206}
SDSS1206 is a special system -- the AGN is a doubly images while most of the host is falls inside the inner caustic thus being quadruply imaged. We consider the galaxy triplet group at the north-west and use a single SIS model to denote their over all mass perturbations. Moreover, as noted by Simon[], a sub-clump is located in the north which is hardly visible  (i.e., Figure 1 in that paper). We model it as a SIS mass model and circular \sersic\ light model with joint centroids. Though we see the visible residuals in the fitted arcs using a single \sersic\ model, we find a double \sersic\ could help significantly improve the goodness of the fitting. Thus, we adopt the single \sersic\ model in our final inference.

@@

\subsubsection{HS2209}
HS2209 imaging data have two visits. We modelled both two visited drizzling data.
The inference of this system is summarized in Figure~\ref{fig:image_inference}-(g). \ding{The host magnitude might be overestimated. The QSO is over bright with a positive background light. Xuheng is Re-fitting this image.}

@@

\begin{table*}
\renewcommand{\arraystretch}{1.25}
%\setlength{\tabcolsep}{20pt}
\centering
  \begin{threeparttable}
\caption{Summary of lensed AGN inference.}\label{tab:host_measure}    
%\resizebox{12cm}{!}{
     \begin{tabular}{cccccccc}
\hline     
(1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) \\    
Object ID & intrinsic Magnitude & Magnitude & Flux Ratio (to Total) & \reff\ & \sersic\ $n$ & adopted AGE & $\log (M_{*}$)  \\
 & (source plane) & (image plane) & ($\%$) & (arcsec) & & (Gyr) & (M$_{\odot}$) \\ \hline
HE0435 & $21.49\substack{+0.40\\-0.29}$ & $18.58\substack{+0.30\\-0.23}$ & $36.0\pm11.1$ & $0.28\pm0.02$ & $2.71\pm0.20$ & $1.50$ & $10.91\substack{+0.12\\-0.16}$ \\
RXJ1131$_{\rm bulge}$ & $21.80\substack{+0.23\\-0.19}$ & $18.70\substack{+0.07\\-0.06}$ & $7.1\pm1.4$ & $0.13\pm0.02$ & fix to 4 & $3.00$ & $10.39\substack{+0.08\\-0.09}$ \\
RXJ1131$_{\rm disk}$ & $19.33\substack{+0.17\\-0.15}$ & $17.14\substack{+0.08\\-0.07}$ & $69.2\pm10.1$ & $0.90\pm0.06$ & fix to 1 & $1.50$ & $11.08\substack{+0.06\\-0.07}$ \\
WFI2033 & $21.78\substack{+0.28\\-0.23}$ & $19.07\substack{+0.35\\-0.26}$ & $19.6\pm4.5$ & $0.28\pm0.02$ & $0.52\pm0.01$ & $0.62$ & $10.51\substack{+0.09\\-0.11}$ \\
SDSS1206 & $21.31\substack{+0.23\\-0.19}$ & $18.30\substack{+0.05\\-0.05}$ & $33.3\pm6.4$ & $0.11\pm0.02$ & $4.57\pm0.53$ & $0.62$ & $10.77\substack{+0.08\\-0.09}$ \\
HE1104 & $21.25\substack{+0.16\\-0.14}$ & $19.16\substack{+0.02\\-0.02}$ & $14.0\pm2.0$ & $0.27\pm0.02$ & $1.05\pm0.04$ & $0.63$ & $11.05\substack{+0.06\\-0.07}$ \\
SDSS0246 & $23.44\substack{+0.28\\-0.22}$ & $20.85\substack{+0.08\\-0.07}$ & $4.0\pm0.9$ & $0.44\pm0.08$ & $4.96\pm0.08$ & $0.63$ & $10.75\substack{+0.09\\-0.11}$ \\
HS2209 & $20.72\substack{+0.26\\-0.21}$ & $19.20\substack{+0.04\\-0.04}$ & $12.5\pm2.7$ & $1.96\pm1.28$ & $3.15\pm1.40$ & $1.00$ & $11.04\substack{+0.08\\-0.10}$ \\
HE0047 & $22.92\substack{+0.48\\-0.33}$ & $20.37\substack{+0.20\\-0.17}$ & $2.3\pm0.8$ & $0.32\pm0.15$ & $4.18\pm0.75$ & $0.62$ & $10.91\substack{+0.13\\-0.19}$ \\
\hline
\end{tabular}
%}
\begin{tablenotes}
      \small
      \item Note: $-$ If any
\end{tablenotes}    
\end{threeparttable}
\end{table*}

@@

\subsection{Stellar population and mass}\label{sec:mstar}
%[] Color inference for the first three cases to decide their stellar template. 
Besides the band we imaging data at the given band we studied in last section, some of the systems also have other band observations by the \hst, which provides the color information of the host galaxy. Given that the other band data has less exposure time with lower single to noise level, we highlight that we only study the color to find a decent stellar template. Then, it would be adopted to the host photometry obtained in last section to infer the final stellar mass.

{\bf HE0435} ~ Besides the imaging data by F160W, this system has also been observed by the \hst\ through F814W and F555W band. We adopted the same approach to modelling the data separately at these two band. % The inferred host magnitudes are xxx and xxx, respectively.
Considering that the lensed host in the image plane is majorly inferred by the subtraction of the AGNs and deflectors light, which it is less dependent on the lens model. We expect it can be obtained with more accuracy. Thus, we infer the color based on the magnitude of the lensed arcs in the image plane. We use {\sc Gsf} code to fit the magnitude of the lensed host and find a 1.5 Gyr stellar template with solar metallicity could well match this color. More details of the information could be found in the Appendix~\ref{app:HE0435}.

{\bf RXJ1131} ~ For this system, the lensed arc is very extended in the image plane which is resolved to the AGNs, one could directly perform the SED fitting of the arc in the image plane. Combining the \hst\ imaging data through three filter F814W and F555W and F160W, we inference the color and we adopt the stellar templates 3 Gyr and 1.5 Gyr with solar metallicity stellar to its bulge and disk, respectively (see Appendix~\ref{app:RXJ1131} for the inference).

{\bf WFI2033} ~ Besides the F160W filter, four other filters including F125W, F140W, F555W, F814W are also available in the \hst\ archive, which has been employed to obtain the color of the host galaxy. We perform the lens model inference for all the filter and infer the host color through five band in the image plane. We find a stellar template with 0.625 Gyr could well match their color (Appendix~\ref{app:WFI2033}).

{\bf HE1104 and the other systems} ~ The imaging data of HE1104 has been observed through F555W and F814W band. However, given limited exposure time, the signal of the lensed arcs is too faint to be detected at this two bands. Due to this limitation, we couldn't infer the color of the host for HE1104. For this case, the other systems, we adopt the criteria by Ding2020[] to assign their stellar population, i.e., the 1 Gyr and 0.625 Gyr stellar population would be adopted for systems as $z<1.44$ and $z>1.44$, respectively.

A summary of the adopted stellar populations is given in Table~\ref{tab:host_measure}, column~(7). Applying these templates to the filter magnitudes obtained in last section, we obtain the stellar mass of our system. Considering that we have obtained very consistent host photometry for the HE0435, RXJ1131 and WFI2033 to previous results using the independent approach, the fidelity of the inferred magnitude are considered to be high. The uncertainty of the \mstar\ estimation are considered as the typical level $0.2$~dex. Same as the comparison, we expect that the uncertainty of the \mbh\ would dominate the error budget in the overall scaling relation obtained in next section.

\subsection{The \mbh-\mstar\ relation}\label{sec:relation}
Having obtained the \mstar\ of each individual system, we combine them with their \mbh\ to reveal the scaling relations. We expect to compare our high redshift lensed sample to the comparison sample as introduced in Section~\ref{sec:sample_select}. We plot the entire measurement together with and present in Figures~\ref{fig:scaling_relation}-(a). Following~\citet{Ding2020}, we fit the \mbh-\mstar\ data with a linear relation as:
\begin{eqnarray}
\label{eq:MMlocal}
\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{M_*}{10^{10}M_{\odot}}).
\end {eqnarray}
We find that our lensed systems appeared to have a slimier offset to the local relations which is consistent to the 32 QSOs by~\citet{Ding2020} at similar redshift range.

To this evolution trend based on the sample redshift, we parameterize the evolution term as the linear relation by:
\begin{eqnarray}
\label{eq:offset}
\Delta \log \mathcal M_{\rm BH}= \gamma \log (1 + z),
\end{eqnarray} 
from which we recover the offset plot, i.e., Figure~8, in~\citet{Ding2020}. We then add the measurements by our lensed systems and show in Figure~\ref{fig:scaling_relation}-(b). We find that the evolution of the offset our sample are well matched to the evolution trend as discovered by the previous inference. Given that we only obtain the measurements from eight lens systems, it is insufficient to fit the offset value quantitively. Nevertheless, the obvious consistency between the sample confirm the fidelity of our measurement and verify previous offset conclusions by~\citet{Ding2020}.

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[height=0.5\textwidth]{fig/MBH-Mstar.pdf}}&
{\includegraphics[height=0.5\textwidth]{fig/MBH-Mstar_vz.pdf}}\\
\end{tabular}
\caption{\label{fig:scaling_relation} 
\todo{This Figures are still ugly so far, which need to be updated.}}
\end{figure*}

@@

Finally, we did not consider the selection effect. Besides the mass function, the selection function of the lensed AGNs is also non-trivial. We note that these effects will have to be modelled in the future if the lensed sample is used to infer the evolution.

@@

\section{Color inference of the host}
We describe the details of the stellar population inference in this section. The template would be then adopted to the photometry by Section~\ref{sec:photometry} to infer the stellar mass.
\subsection{HE0435}\label{app:HE0435}
The HE0435 system are also modelled through ACS/F814W and ACS/F555W (GO-9744; PI: C. S. Kochanek). We derive the magnitude of the lensed galaxy and infer the color of the host in the image plane. We illustrate the lens model for the other two band in Figure~\ref{fig:app_HE0435}. The inferred magnitude of the host galaxy in the image plane is quite robust. Having obtained the magnitude of the lensed host at three band, we use {\sc gsf} package to select the best stellar population from a range of [0.625, 0.8, 1.0, 1.5, 2.0, 3.0] Gyr with solar metallicity. Finally, a template with ago of 1.5 Gyr is selected.

\begin{figure*}
\centering
\subfloat[HE0435 F555W]{\includegraphics[ width=0.8\textwidth]{fig/HE0435_f555w_inference.pdf}}\\
\subfloat[HE0435 F814W]{\includegraphics[ width=0.8\textwidth]{fig/HE0435_f814w_inference.pdf}}
\caption{\label{fig:app_HE0435} 
Illustrations of the inference of HE0435 at the other two band. }
\end{figure*}

\subsection{RXJ1131}\label{app:RXJ1131}
Using the three band data including  ACS/F814W and ACS/F555W and NIC2/F160W (GO-9744; PI: C. S. Kochanek), we preform the SED fitting in the imaging plane directly pixel by pixel in Figure~\ref{fig:app_RXJ1131}. \ding{This part is actually done by Takahiro in~\citep{Ding2017b}. The image of the fitted age looks noisy, but it is in the range of the [9.25 - 9.50] (logAge), i.e. [1.5, 3.0] (Gyr). We can remove this A2 but only mention the fitting is done 2017 in that paper.}
\begin{figure}
\centering
{\includegraphics[width=0.25\textwidth]{fig/map_age_zRXJ_1131.pdf}}\\
\caption{\label{fig:app_RXJ1131} 
Illustrations of the SED fitting of the galaxy age pixel by pixel.  }
\end{figure}

\subsection{WFI2033}\label{app:WFI2033}
WFI2033 is also observed by other four band data including WFC3/F125W (GO-12874; PI: D. Floyd), WFC3/F140W (GO-13732; PI: A. Nierenberg), ACS/F555W+F814W  (GO-9744; PI: C. S. Kochanek). The data quality by F125W is limited by its exposure time; and the host information is not well extracted. We does not take it into account in the color inference. 
Similar to Section~\ref{app:HE0435}, the lensed color of WFI2033 has been modelled through five band. The lensed models are presented in the~Figure~\ref{fig:app_WFI2033}.
